A brief comparison of speed of Interior Point and EM algorithms

### 2017-01-15 analysis/IPvsEM.Rmd
Re-rendered summarize_coverage.Rmd and summarize_dsc_znull.Rmd after updates given in above commits.

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
source("chunk-options.R")
```

>>>>

First, we load the necessary libraries.

```{r packages}
library(REBayes)
library(ashr)
library(ggplot2)
```

```{r chunk_options, include=FALSE}
# Specify settings for displaying the plots in the rendered document.
source("chunk-options.R")
```
